Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-12 main_paper.tex
More tweaks

We include two other procedures for comparison: CCT's bias-corrected interval
and a ``naive'' uncorrected estimator. We
estimate CCT's bias corrected procedure with AMSE-optimal bandwidth and estimate
the ``naive'' uncorrected interval with the optimal bandwidth $h$ proposed by
\cite{IK}. We use triangular kernel through out all the three procedures to facilitate direct comparisons.\footnote{%
Simulation results for other kernels and variance estimators are similar and
available upon request.} %

@@

Table~\ref{tbl:1} presents the results of these simulations. It consists of two panels, with results for homoskedastic data in Panel A and heteroskedastic data in Panel B. The row labeled
``wild bootstrap'' shows results for our proposed bootstrap interval; ``CCT'' shows
results for the analytically-corrected interval and ``Naive'' shows results for analytically-uncorrected interval. The first three columns give the bias,
standard deviation, and Root-MSE of the point
estimators corresponding to each approach.  As expected, both
bias corrected estimators have
bias close to zero, with their standard deviation largely
determining the estimators' RMSE. Moreover, as Theorem~\ref{T1} suggests, the
bootstrap and analytically-corrected estimators have essentially the same
standard deviation across all of the DGPs.

>>>>

We include two other procedures for comparison: CCT's bias-corrected interval and a ``naive'' uncorrected estimator.
 We estimate CCT's bias corrected procedure with AMSE-optimal bandwidth and estimate
the ``naive'' uncorrected interval with the optimal bandwidth $h$ proposed by
\cite{IK}. We use triangular kernel throughout all the three procedures to facilitate direct comparisons.\footnote{%
Simulation results for other kernels and variance estimators produced similar outcomes.} %

@@

Table~\ref{tbl:1} presents the results of these simulations. It consists of two panels, with results for homoskedastic data in Panel A and heteroskedastic data in Panel B. The row labeled
``Wild bootstrap'' shows results for our proposed bootstrap based interval; ``CCT'' shows
results for the analytically-corrected interval and ``Naive'' shows results for analytically-uncorrected interval. The first three columns give the bias,
standard deviation, and Root-MSE of the point
estimators corresponding to each approach.  As expected, both
bias corrected estimators have
bias close to zero, with their standard deviation largely
determining the estimators' RMSE. Moreover, as Theorem~\ref{T1} suggests, the
bootstrap and analytically-corrected estimators have essentially the same
standard deviation across all of the DGPs.
